\vspace{-1.5cm} \textbf{STA610 Case Study 1 Team 4 Report}

### 2021-03-22 final_report_2.Rmd
limitations edit

We performed an initial examination of two grouping variables, `state` and `USA_region`. The state North Dakota had only one observation, and as such was not considered a well-defined "group" for which a variance could be estimated; thus this state's observation was removed. States labeled simply as "USA" were recoded to "Unknown". Region was also sometimes labeled as uknown or other; these observations coincided with the unknown states (see appendix Table X). (The variable `city` as a grouping variable is addressed later in the report.)

@@

@@

## Visualizations

>>>>

We performed an initial examination of two grouping variables, `state` and `USA_region`. The state North Dakota had only one observation, and as such was not considered a well-defined "group" for which a variance could be estimated; thus this state's observation was removed. States labeled simply as "USA" were recoded to "Unknown". Region was also sometimes labeled as uknown or other; these observations coincided with the unknown states (see appendix). (The variable `city` as a grouping variable is addressed later in the report.)

@@

Our analysis has several limitations. Our filtering of the `log_ppm` variable to non-extreme values must be kept in mind, as we are essentially modeling typical values only, so some unusual price values may not be predicted correctly by our model. Small sample sizes for some states are not ideal, although our hierarchical model structure helps to mitigate this issue. User-input data is naturally messy and should be taken with a grain of salt. Furthermore, our sample is essentially self-selected (people who choose to enter their data into the StreetRx web site) rather than randomly sampled, and this may affect the generalizability of our results.

@@

## Visualizations, etc.

```{r}
#the state-by-region table of coutns below
table(df$state, df$USA_region)
```
